Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-06-06 ms.qmd
Added in details on future climate reductions in variance

Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` populations). Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-fig6 A-C). Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showing an increase (@fig-fig6 D). Out of the `r length(unique(all_pred2$match))` populations variance was predicted to decrease in `r (sum(decreases$n, na.rm = TRUE) / length(decreases$n[complete.cases(decreases$n)]))*100`% of the locations. Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).

>>>>

Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r length(unique(all_pred$spp))`, from `r length(unique(all_pred$uniques))` populations). Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-fig6 A-C). Projected changes in the opportunity for selection were highly variable across the globe, with some regions showing a decrease in the opportunity for selection, while others showing an increase (@fig-fig6 D). Out of the `r length(unique(all_pred2$match))` populations variance was predicted to decrease in `r (sum(decreases$n, na.rm = TRUE) / length(decreases$n[complete.cases(decreases$n)]))*100`% of the locations. Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`). Across habitat types climate change is predicted to result in a only a `r lapply(mean_perc_habitat, mean)$f`% change in variance for freshwater systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$f[2]`%), whereas we expect a `r abs(lapply(mean_perc_habitat, mean)$m)`% reduction in variance for marine systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$m[2]`%) and a `r abs(lapply(mean_perc_habitat, mean)$t)`% reduction in variance for terrestrial systems (95% CI: `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[1]` to `r lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))$t[2]`%) under a RCP8.5 climate scenerio.
